EOBS Climate data

### 2017-12-27 analysis/prepare_eobs_data.Rmd
try treeclim data

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
```

@@

```{r}
eobs <- read.csv(file=paste0(di, 'data_raw/eobs/eobs_data_robles.csv'), header=TRUE, sep=',')

@@

>>>>

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("treeclim")
```

@@

```{r}
eobs <- read.csv(file=paste0(di, 'data_raw/eobs/eobs_data_robles.csv'), header=TRUE, sep=',')
cro <- read.csv(file=paste(di, "data/cronos_medias/cronos_sites_rwi.csv", sep=""), header=TRUE, sep=',')

croN <- cro %>% filter(site == 'sj') %>% dplyr::select(-site) %>% 
  filter(year > 1949)
rownames(croN) <- croN$year

@@

cl <- eobs %>% 
  filter(loc == 'N') %>% 
  filter(variable %in% c('rr', 'tg')) %>% 
  dplyr::select(value, variable, year, month) %>% 
  spread(variable, value)

cl <- cl %>% rename(prec = rr, temp = tg) %>% 
  filter(year < 2017)

test <- dcc(chrono = croN, climate = cl)

croN 
# http://czang.org/treeclim.html
